---
title: "Simulations for Interim Analysis"
date: today
format: 
  html:
    embed-resources: true
code-fold: true
params:
  prior_std: 0.25
  n_per_arm: 400
  total_sims: 25
  num_workers: 1
---

```{r}
#| output: false
library(umdorthotrialplanning)
library(dplyr)
library(ggplot2)
library(BuyseTest)
library(cmdstanr)
library(furrr)
library(ggalluvial)

if (!"params" %in% ls()) {
  params <- list(
    prior_std = .25,
    n_per_arm = 400,
    total_sims = 25,
    num_workers = 1
  )
}
```

```{r}
make_stan_data <- function(x, prior_mean = 0, prior_std = 1) {
  list(
    # transformations based on u - statistic
    win_ratio = log(x$estimate),
    win_ratio_ste = x$std.error / x$estimate,
    prior_mean = prior_mean,
    prior_std = prior_std
  )
}

hit_success <- function(x) {
  data.frame(
    hd_superiority1 = x$pr_treatment_benefit > .99,
    hd_superiority2 = x$pr_wr_15 > .90,
    hd_inferiority = x$pr_treatment_benefit < .01,
    hd_equivalence =
      x$pr_equivalence_hd > .9 &
        x$pr_treatment_benefit > 1 / 3 &
        x$pr_treatment_benefit < 2 / 3,
    hd_equivalencesuperiority =
      x$pr_equivalence_hd > .9 &
        x$pr_treatment_benefit > 2 / 3,
    hd_equivalenceinferiority =
      x$pr_equivalence_hd > .9 &
        x$pr_treatment_benefit < 1 / 3,
    ld_superiority1 = x$pr_treatment_benefit > .975,
    ld_superiority2 = x$pr_wr_13 > .90,
    ld_inferiority = x$pr_treatment_benefit < .025,
    ld_equivalence = x$pr_equivalence > .9 &
      x$pr_treatment_benefit > 1 / 3 &
      x$pr_treatment_benefit < 2 / 3,
    ld_equivalencesuperiority =
      x$pr_equivalence > .9 &
        x$pr_treatment_benefit > 2 / 3,
    ld_equivalenceinferiority =
      x$pr_equivalence > .9 &
        x$pr_treatment_benefit < 1 / 3
  )
}

stan_success <- function(fit) {
  summary_vals <- fit$summary("theta",
    pr_treatment_benefit = ~ mean(. > 1),
    pr_wr_15 = ~ mean(. > 1.5),
    pr_wr_13 = ~ mean(. > 1.3),
    pr_equivalence = ~ mean(. > 1 / 1.3 & . < 1.3),
    pr_equivalence_hd = ~ mean(. > .8 & . < 1.25)
  )
  out <- hit_success(summary_vals)
  out$win_ratio <- fit$summary(variables = "theta")$mean
  out
}
subset_trial <- function(n_per_arm = 50, d) {
  total_subj <- nrow(d)
  if (n_per_arm * 2 > total_subj) {
    stop("Cannot subset more than exists")
  }

  part_1 <- 1:n_per_arm
  part_2 <- part_1 + total_subj / 2
  d[c(part_1, part_2), ]
}

summarize_results <- function(x) {
  x |>
    mutate(analysis_amount = as.numeric(analysis_amount)) |>
    group_by(.sim) |>
    mutate(across(c(matches("^[lh]d_")), function(x) cumsum(x) > 0L)) |>
    group_by(analysis_amount) |>
    summarise(across(-.sim, mean))
}

bayesian_trial_raw_results <- function(
  n_per_arm, data_cuts, mod, ..., seed = NULL, alpha = .05,
  prior_std = 1,
  freq_outputs = FALSE
) {
  if (!is.null(seed)) {
    set.seed(seed)
  }

  all_trial_data <- simulate_trial(n_per_arm = n_per_arm, ...)
  data_subsets <- purrr::map(data_cuts, subset_trial, d = all_trial_data)


  if (freq_outputs) {
    freq_estimates <- data_subsets |>
      purrr::map(estimate_dataset) |>
      purrr::map(function(x) subset(x, term == "days_at_home_t7"))
    return(freq_estimates)
  } else {
    freq_estimates <- data_subsets |>
      purrr::map(estimate_dataset, alpha = alpha) |>
      purrr::map(function(x) subset(x, term == "days_at_home_t7", select = c(estimate, std.error)))
  }

  trial_output <- purrr::map(freq_estimates, function(x) {
    fit <- mod$sample(
      data = make_stan_data(x, prior_std = prior_std),
      # seed = 123,
      chains = 1,
      parallel_chains = 1,
      refresh = 0,
      show_messages = FALSE
    )
    fit
    # stan_success(fit)
  })

  trial_output
}

make_seeds <- function(n) {
  as.integer(runif(n, min = 1e6, max = 1e7 - 1))
}

compute_trial_stop <- function(x, prefix = c("hd", "ld")) {
  prefix <- match.arg(prefix)
  col_to_check <- paste(prefix, c("superiority1", "superiority2", "inferiority", "equivalence", "equivalencesuperiority", "equivalenceinferiority"), sep = "_")

  all_stops <- sapply(x[, col_to_check], function(y) {
    x$analysis_amount[which(y)[1]]
  })

  trial_result <- all_stops[which.min(all_stops)]


  if (length(trial_result) != 1) {
    out <- data.frame(
      stopping_rule = "No Conclusion",
      stopping_subjects = max(x$analysis_amount),
      stopping_win_ratio = tail(x$win_ratio, 1)
    )
  } else {
    win_ratio <- which(unname(trial_result) == x$analysis_amount)
    win_ratio <- x$win_ratio[win_ratio]

    out <- data.frame(
      stopping_rule = names(trial_result),
      stopping_subjects = unname(trial_result),
      stopping_win_ratio = win_ratio
    )
  }
  out
}


file <- system.file("stanmod", "meta.stan", package = "umdorthotrialplanning")
dir.create(tools::R_user_dir("umdorthotrialplanning"), recursive = TRUE, showWarnings = F)
mod <- cmdstan_model(file, dir = tools::R_user_dir("umdorthotrialplanning"))
```

```{r}
set.seed(20250223)

n_per_arm <- params$n_per_arm
data_cuts <- seq(50, n_per_arm, by = 25)
names(data_cuts) <- data_cuts
prior_std <- params$prior_std


total_sims <- params$total_sims
sim_params <- tibble::tibble(
  n_per_arm = n_per_arm,
  data_cuts = list(data_cuts),
  seed = make_seeds(total_sims)
)

plan(multicore, workers = params$num_workers)
```


```{r}
# cm <- cachem::cache_disk(dir = here::here(".cache", "bayesian_trial_raw_results"))
# bayesian_trial_raw_results <- memoise::memoise(bayesian_trial_raw_results, cache = cm)
```

## Simulation Overiew

The simulations look at a trial with 400 total subjects (200/arm). An interim look is taken as soon as 50 subjects are available in each arm, and then repeated every 50 subjects until the full enrollment occurs. 

At each look, the following criteria are used:


| **High differentiation comparison** |             |                                                   |
| ----------------------------------- | ----------- | ------------------------------------------------- |
| id                                  | **Type**    | **Threshold**                                     |
| hd_superiority1                     | Superiority | 99% probability of treatment benefit              |
| hd_superiority2                     |             | 90% probability of win ratio > 1.5                |
| hd_inferiority                      | Inferiority | 1% probability of treatment benefit               |
| hd_equivalence                      | Equivalence | 90% probability between win ratio of 0.8 and 1.25 |


| **Low differentiation comparison** |             |                                                   |
| ---------------------------------- | ----------- | ------------------------------------------------- |
| id                                 | **Type**    | **Threshold**                                     |
| ld_superiority1                    | Superiority | 97.5% probability of treatment benefit            |
| ld_superiority2                    |             | 90% probability of win ratio > 1.3                |
| ld_inferiority                     | Inferiority | 2.5% probability of treatment benefit             |
| ld_equivalence                     | Equivalence | 90% probability between win ratio of 0.77 and 1.3 |


Simulations under the alternative hypothesis were run using the previously defined assumed rates:

|                  | Control | Active | Active (Low Differentiation) |
| ---------------- | ------- | ------ | -----
| Survival         | .85     | .9     | .9 |
| Days at home     | 67      | 78     | 70 |
| Amb Status Shift |         | 0.2    | 0.1 |


Additionally, a null hypothesis were also performed to see what type I error rates were.


`r total_sims` simulations were run for each scenario.

## Results

The tables below show the rates for the number of times each criteria is hit. The rates are cumulative - so if superiority is hit with 50, it will automatically hit at 100, 150, and 200.
Additionally branching logic is not implemented. For example if inferiority is hit at 50, the trial does not stop.

### Alternative Hypothesis Results - High Differentiation


```{r}
#| warning: false
sim_calcs <- sim_params |>
  furrr::future_pmap(bayesian_trial_raw_results,
    mod = mod,
    prior_std = prior_std,
    .options = furrr_options(seed = TRUE),
    .progress = interactive()
  )
```


```{r}
sim_results <- purrr::map(
  sim_calcs,
  function(x) purrr::map(x, stan_success) |> purrr::list_rbind(names_to = "analysis_amount")
) |> purrr::list_rbind(names_to = ".sim")
sim_results$analysis_amount <- as.numeric(sim_results$analysis_amount)
```

```{r}
sim_results |>
  summarize_results() |>
  flextable::flextable()
```

The following table shows why trials stopped (No Conclusions is used if none of the criteria are met). The average trial size for each conclusion and overall are shown. Only the high differentiation are shown here since this trial has high power.


```{r}
all_res_temp <- sim_results |>
  split(~.sim) |>
  purrr::map(compute_trial_stop, prefix = "hd") |>
  purrr::list_rbind() |>
  mutate(stopping_rule = if_else(stopping_rule == "No Conclusion", paste0("hd", "_No Conclusion"), stopping_rule)) |>
  tidyr::separate(stopping_rule, into = c("group", "rule"), sep = "_")

dplyr::bind_rows(all_res_temp, all_res_temp |> mutate(rule = "Overall")) |>
  dplyr::mutate(
    rule = factor(rule),
    rule = forcats::fct_relevel(rule, "Overall", after = Inf)
  ) |>
  group_by(group, rule) |>
  summarise(
    total_stops = n(),
    average_size = mean(stopping_subjects),
    average_win_ratio = mean(stopping_win_ratio),
    trials_stopped_by_90 = quantile(stopping_subjects, .9),
    trials_stopped_by_95 = quantile(stopping_subjects, .95),
    .groups = "drop"
  ) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group = "Group",
    rule = "Rule",
    total_stops = "Total Stops",
    average_size = "Average Size",
    average_win_ratio = "Average Win Ratio",
    trials_stopped_by_90 = "90% of Trials Stopped",
    trials_stopped_by_95 = "95% of Trials Stopped"
  )


dplyr::bind_rows(all_res_temp, all_res_temp |> mutate(rule = "Overall")) |>
  dplyr::mutate(
    rule = factor(rule),
    rule = forcats::fct_relevel(rule, "Overall", after = Inf)
  ) |>
  filter(rule != "Overall") |>
  group_by(group, rule) |>
  ggplot(aes(color = rule, x = stopping_subjects, stopping_win_ratio)) +
  geom_point(alpha = .5) +
  theme_bw()


```


The following diagram shows the flow of when different criteria are hit at each sample size. Note that the `NA` stratum represents trials that have already been stopped.

```{r}

alluvial_df <- sim_results |>
  split(~.sim) |>
  purrr::map(compute_trial_stop, prefix = "hd") |>
  purrr::list_rbind(names_to = ".sim") |>
  select(-stopping_win_ratio) |>
  tidyr::expand_grid(all_cuts = data_cuts) |>
  group_by(.sim) |>
  filter(all_cuts <= stopping_subjects) |>
  mutate(stopping_rule = if_else(all_cuts < stopping_subjects, "No Conclusion", stopping_rule)) |>
  ungroup() |>
  mutate(
    stopping_rule = factor(stopping_rule),
    stopping_rule = forcats::fct_relevel(stopping_rule, "No Conclusion")
  ) |>
  select(-stopping_subjects) |>
  tidyr::pivot_wider(names_from = all_cuts, values_from = stopping_rule) |>
  group_by(across(-.sim)) |>
  summarise(Freq = n(), .groups = "drop")

alluvial_df |>
  to_lodes_form(key = "Trial Size", axes = seq_len(ncol(alluvial_df) - 1)) |>
  ggplot() +
  aes(x = `Trial Size`, stratum = stratum, alluvium = alluvium, label = stratum, y = Freq) +
  geom_alluvium(fill = "lightblue") +
  geom_stratum(aes(fill = stratum)) +
  # geom_text(stat = "stratum", angle = 90) +
  theme_minimal()

```


### Alternative Hypothesis - Low Differentiation

```{r}
#| warning: false

sim_calcs <- sim_params |>
  furrr::future_pmap(bayesian_trial_raw_results,
    mod = mod,
    days_at_home_mean = c(67, 70),
    amb_status_latent_shift = .1,
    prior_std = prior_std,
    .options = furrr_options(seed = TRUE),
    .progress = interactive()
  )
```


```{r}
sim_results <- purrr::map(
  sim_calcs,
  function(x) purrr::map(x, stan_success) |> purrr::list_rbind(names_to = "analysis_amount")
) |> purrr::list_rbind(names_to = ".sim")
sim_results$analysis_amount <- as.numeric(sim_results$analysis_amount)
```

```{r}
sim_results |>
  summarize_results() |>
  flextable::flextable()
```

The following table shows why trials stopped (No Conclusions is used if none of the criteria are met). The average trial size for each conclusion and overall are shown. Only the low differentiation are shown here.

```{r}
all_res_temp <- sim_results |>
  split(~.sim) |>
  purrr::map(compute_trial_stop, prefix = "ld") |>
  purrr::list_rbind() |>
  tidyr::separate(stopping_rule, into = c("group", "rule"))

dplyr::bind_rows(all_res_temp, all_res_temp |> mutate(rule = "Overall")) |>
  dplyr::mutate(
    rule = factor(rule),
    rule = forcats::fct_relevel(rule, "Overall", after = Inf)
  ) |>
  group_by(group, rule) |>
  summarise(
    total_stops = n(),
    average_size = mean(stopping_subjects),
    average_win_ratio = mean(stopping_win_ratio),
    trials_stopped_by_90 = quantile(stopping_subjects, .9),
    trials_stopped_by_95 = quantile(stopping_subjects, .95),
    .groups = "drop"
  ) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group = "Group",
    rule = "Rule",
    total_stops = "Total Stops",
    average_size = "Average Size",
    average_win_ratio = "Average Win Ratio",
    trials_stopped_by_90 = "90% of Trials Stopped",
    trials_stopped_by_95 = "95% of Trials Stopped"
  )

dplyr::bind_rows(all_res_temp, all_res_temp |> mutate(rule = "Overall")) |>
  dplyr::mutate(
    rule = factor(rule),
    rule = forcats::fct_relevel(rule, "Overall", after = Inf)
  ) |>
  filter(rule != "Overall") |>
  group_by(group, rule) |>
  ggplot(aes(color = rule, x = stopping_subjects, stopping_win_ratio)) +
  geom_point(alpha = .5) +
  theme_bw()


```


The following diagram shows the flow of when different criteria are hit at each sample size. Note that the `NA` stratum represents trials that have already been stopped.

```{r}

alluvial_df <- sim_results |>
  split(~.sim) |>
  purrr::map(compute_trial_stop, prefix = "ld") |>
  purrr::list_rbind(names_to = ".sim") |>
  select(-stopping_win_ratio) |>
  tidyr::expand_grid(all_cuts = data_cuts) |>
  group_by(.sim) |>
  filter(all_cuts <= stopping_subjects) |>
  mutate(stopping_rule = if_else(all_cuts < stopping_subjects, "No Conclusion", stopping_rule)) |>
  ungroup() |>
  mutate(
    stopping_rule = factor(stopping_rule),
    stopping_rule = forcats::fct_relevel(stopping_rule, "No Conclusion")
  ) |>
  select(-stopping_subjects) |>
  tidyr::pivot_wider(names_from = all_cuts, values_from = stopping_rule) |>
  group_by(across(-.sim)) |>
  summarise(Freq = n(), .groups = "drop")

alluvial_df |>
  to_lodes_form(key = "Trial Size", axes = seq_len(ncol(alluvial_df) - 1)) |>
  ggplot() +
  aes(x = `Trial Size`, stratum = stratum, alluvium = alluvium, label = stratum, y = Freq) +
  geom_alluvium(fill = "lightblue") +
  geom_stratum(aes(fill = stratum)) +
  # geom_text(stat = "stratum", angle = 90) +
  theme_minimal()

```

### Null Hypothesis Results

```{r}
#| warning: false
null_sim_calcs <- sim_params |>
  furrr::future_pmap(bayesian_trial_raw_results,
    mod = mod,
    prior_std = prior_std,
    survival_prob = c(.85, .85),
    days_at_home_mean = c(70, 70),
    amb_status_latent_shift = 0,
    .options = furrr_options(seed = TRUE),
    .progress = interactive()
  )

```

```{r}
null_sim_results <- purrr::map(
  null_sim_calcs,
  function(x) {
    purrr::map(x, stan_success) |>
      purrr::list_rbind(names_to = "analysis_amount")
  }
) |> purrr::list_rbind(names_to = ".sim")
null_sim_results$analysis_amount <- as.numeric(null_sim_results$analysis_amount)
```

```{r}
null_sim_results |>
  summarize_results() |>
  flextable::flextable()

```


```{r}
x <- purrr::map(purrr::set_names(c("hd", "ld")), function(.c) {
  res_temp <- null_sim_results |>
    split(~.sim) |>
    purrr::map(compute_trial_stop, prefix = .c) |>
    purrr::list_rbind() |>
    mutate(stopping_rule = if_else(stopping_rule == "No Conclusion", paste0(.c, "_No Conclusion"), stopping_rule)) |>
    tidyr::separate(stopping_rule, into = c("group", "rule"), sep = "_")
  dplyr::bind_rows(res_temp, res_temp |> mutate(rule = "Overall"))
}) |>
  purrr::list_rbind() |>
  dplyr::mutate(
    rule = factor(rule),
    rule = forcats::fct_relevel(rule, "Overall", after = Inf)
  )


x |>
  group_by(group, rule) |>
  summarise(
    total_stops = n(),
    average_size = mean(stopping_subjects),
    average_win_ratio = mean(stopping_win_ratio),
    trials_stopped_by_90 = quantile(stopping_subjects, .9),
    trials_stopped_by_95 = quantile(stopping_subjects, .95),
    .groups = "drop"
  ) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group = "Group",
    rule = "Rule",
    total_stops = "Total Stops",
    average_size = "Average Size",
    average_win_ratio = "Average Win Ratio",
    trials_stopped_by_90 = "90% of Trials Stopped",
    trials_stopped_by_95 = "95% of Trials Stopped"
  )


x |>
  filter(rule != "Overall") |>
  # group_by(group, rule) |>
  ggplot(aes(color = rule, x = stopping_subjects, stopping_win_ratio)) +
  geom_point(alpha = .5) +
  theme_bw() +
  facet_wrap(~group)

```


```{r}

alluvial_df <- null_sim_results |>
  split(~.sim) |>
  purrr::map(compute_trial_stop, prefix = "hd") |>
  purrr::list_rbind(names_to = ".sim") |>
  select(-stopping_win_ratio) |>
  tidyr::expand_grid(all_cuts = data_cuts) |>
  group_by(.sim) |>
  filter(all_cuts <= stopping_subjects) |>
  mutate(stopping_rule = if_else(all_cuts < stopping_subjects, "No Conclusion", stopping_rule)) |>
  ungroup() |>
  mutate(
    stopping_rule = factor(stopping_rule),
    stopping_rule = forcats::fct_relevel(stopping_rule, "No Conclusion")
  ) |>
  select(-stopping_subjects) |>
  tidyr::pivot_wider(names_from = all_cuts, values_from = stopping_rule) |>
  group_by(across(-.sim)) |>
  summarise(Freq = n(), .groups = "drop")

alluvial_df |>
  to_lodes_form(key = "Trial Size", axes = seq_len(ncol(alluvial_df) - 1)) |>
  ggplot() +
  aes(x = `Trial Size`, stratum = stratum, alluvium = alluvium, label = stratum, y = Freq) +
  geom_alluvium(fill = "lightblue") +
  geom_stratum(aes(fill = stratum)) +
  # geom_text(stat = "stratum", angle = 90) +
  theme_minimal()
```


```{r}
alluvial_df <- null_sim_results |>
  split(~.sim) |>
  purrr::map(compute_trial_stop, prefix = "hd") |>
  purrr::list_rbind(names_to = ".sim") |>
  select(-stopping_win_ratio) |>
  tidyr::expand_grid(all_cuts = data_cuts) |>
  group_by(.sim) |>
  filter(all_cuts <= stopping_subjects) |>
  mutate(stopping_rule = if_else(all_cuts < stopping_subjects, "No Conclusion", stopping_rule)) |>
  ungroup() |>
  mutate(
    stopping_rule = factor(stopping_rule),
    stopping_rule = forcats::fct_relevel(stopping_rule, "No Conclusion")
  ) |>
  select(-stopping_subjects) |>
  tidyr::pivot_wider(names_from = all_cuts, values_from = stopping_rule) |>
  group_by(across(-.sim)) |>
  summarise(Freq = n(), .groups = "drop")


alluvial_df |>
  to_lodes_form(key = "Trial Size", axes = seq_len(ncol(alluvial_df) - 1)) |>
  ggplot() +
  aes(x = `Trial Size`, stratum = stratum, alluvium = alluvium, label = stratum, y = Freq) +
  geom_alluvium(fill = "lightblue") +
  geom_stratum(aes(fill = stratum)) +
  # geom_text(stat = "stratum", angle = 90) +
  theme_minimal()

```


### Frequentist Results

The results below just look at the frequentist equivilant of ld_superiority1 and inferiority. The others are set to FALSE for all simulations.

```{r}
#| eval: true

# frequentist analysis code check Bayesian
# results are very similar when a wide prior is set
null_sim_calcs_freq <- sim_params |>
  furrr::future_pmap(bayesian_trial_raw_results,
    mod = mod,
    survival_prob = c(.85, .85),
    days_at_home_mean = c(70, 70),
    amb_status_latent_shift = 0,
    freq_outputs = T,
    alpha = .05,
    .options = furrr_options(seed = TRUE),
    .progress = interactive()
  )


freq_success <- function(x) {
  data.frame(
    ld_superiority1 = x$conf.low > 1,
    ld_inferiority = x$conf.high < 1,
    ld_superiority2 = FALSE,
    ld_equivalence = FALSE,
    ld_equivalencesuperiority = FALSE,
    ld_equivalenceinferiority = FALSE,
    win_ratio = x$estimate
  )
}

null_sim_results_freq <- purrr::map(
  null_sim_calcs_freq,
  function(x) {
    purrr::map(x, freq_success) |>
      purrr::list_rbind(names_to = "analysis_amount")
  }
) |> purrr::list_rbind(names_to = ".sim")
null_sim_results_freq$analysis_amount <- as.numeric(null_sim_results_freq$analysis_amount)

null_sim_results_freq |>
  summarize_results() |>
  dplyr::select(analysis_amount:ld_inferiority, win_ratio) |>
  flextable::flextable()

purrr::map(purrr::set_names(c("ld")), function(.c) {
  null_sim_results_freq |>
    split(~.sim) |>
    purrr::map(compute_trial_stop, prefix = .c) |>
    purrr::list_rbind()
}) |>
  purrr::list_rbind(names_to = "stopping_group") |>
  group_by(stopping_group, stopping_rule) |>
  summarise(
    total_stops = n(),
    average_size = mean(stopping_subjects)
  ) |>
  group_by(stopping_group) |>
  mutate(overall_average_size = weighted.mean(average_size, total_stops))


purrr::map(purrr::set_names(c("ld")), function(.c) {
  res_temp <- null_sim_results_freq |>
    split(~.sim) |>
    purrr::map(compute_trial_stop, prefix = .c) |>
    purrr::list_rbind() |>
    mutate(stopping_rule = if_else(stopping_rule == "No Conclusion", paste0(.c, "_No Conclusion"), stopping_rule)) |>
    tidyr::separate(stopping_rule, into = c("group", "rule"), sep = "_")
  dplyr::bind_rows(res_temp, res_temp |> mutate(rule = "Overall"))
}) |>
  purrr::list_rbind() |>
  dplyr::mutate(
    rule = factor(rule),
    rule = forcats::fct_relevel(rule, "Overall", after = Inf)
  ) |>
  group_by(group, rule) |>
  summarise(
    total_stops = n(),
    average_size = mean(stopping_subjects),
    average_win_ratio = mean(stopping_win_ratio),
    trials_stopped_by_90 = quantile(stopping_subjects, .9),
    trials_stopped_by_95 = quantile(stopping_subjects, .95),
    .groups = "drop"
  ) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group = "Group",
    rule = "Rule",
    total_stops = "Total Stops",
    average_size = "Average Size",
    average_win_ratio = "Average Win Ratio",
    trials_stopped_by_90 = "90% of Trials Stopped",
    trials_stopped_by_95 = "95% of Trials Stopped"
  )
```

