---
title: "Simulations for Interim Analysis"
date: today
format: 
  html:
    embed-resources: true
code-fold: true
---

```{r}
#| output: false
library(dplyr)
library(ggplot2)
library(BuyseTest)
library(cmdstanr)
r_files <- list.files(here::here("R"), full.names = TRUE)
sapply(r_files, source)
```

```{r}
make_stan_data <- function(x, prior_mean = 1, prior_std = 1) {
  list(
    win_ratio = x$estimate,
    win_ratio_ste = x$std.error,
    prior_mean = prior_mean,
    prior_std = prior_std
  )
}

hit_success <- function(x) {
  data.frame(
    hd_superiority1 = x$pr_treatment_benefit > .99,
    hd_superiority2 = x$pr_wr_15 > .90,
    hd_inferiority = x$pr_treatment_benefit < .01,
    hd_equivalence = x$pr_equivalence > .9,
    ld_superiority1 = x$pr_treatment_benefit > .975,
    ld_superiority2 = x$pr_wr_13 > .90,
    ld_inferiority = x$pr_treatment_benefit < .025,
    ld_equivalence = x$pr_equivalence > .9
  )
}

stan_success <- function(fit) {
  summary_vals <- fit$summary("theta",
    pr_treatment_benefit = ~ mean(. > 1),
    pr_wr_15 = ~ mean(. > 1.5),
    pr_wr_13 = ~ mean(. > 1.3),
    pr_equivalence = ~ mean(. > .8 & . < 1.25)
  )
  hit_success(summary_vals)
}
subset_trial <- function(n_per_arm = 50, d) {
  total_subj <- nrow(d)
  if (n_per_arm * 2 > total_subj) {
    stop("Cannot subset more than exists")
  }

  part_1 <- 1:n_per_arm
  part_2 <- part_1 + total_subj / 2
  d[c(part_1, part_2), ]
}

summarize_results <- function(x) {
  x |>
    mutate(analysis_amount = as.numeric(analysis_amount)) |>
    group_by(.sim) |>
    mutate(across(c(matches("^[lh]d_")), function(x) cumsum(x) > 0L)) |>
    group_by(analysis_amount) |>
    summarise(across(-.sim, mean))
}


file <- here::here("inst", "stanmod", "meta.stan")
mod <- cmdstan_model(file)
```

```{r}
set.seed(20250210)

n_per_arm <- 200
data_cuts <- seq(50, n_per_arm, by = 50)
names(data_cuts) <- data_cuts

total_sims <- 1000
```



## Simulation Overiew

The simulations look at a trial with 400 total subjects (200/arm). An interim look is taken as soon as 50 subjects are available in each arm, and then repeated every 50 subjects until the full enrollment occurs. 

At each look, the following criteria are used:


| **High differentiation comparison** |             |                                                   |
| ----------------------------------- | ----------- | ------------------------------------------------- |
| id                                  | **Type**    | **Threshold**                                     |
| hd_superiority1                     | Superiority | 99% probability of treatment benefit              |
| hd_superiority2                     |             | 90% probability of win ratio > 1.5                |
| hd_inferiority                      | Inferiority | 1% probability of treatment benefit               |
| hd_equivalence                      | Equivalence | 90% probability between win ratio of 0.8 and 1.25 |


| **Low differentiation comparison** |             |                                                   |
| ---------------------------------- | ----------- | ------------------------------------------------- |
| id                                 | **Type**    | **Threshold**                                     |
| ld_superiority1                    | Superiority | 97.5% probability of treatment benefit            |
| ld_superiority2                    |             | 90% probability of win ratio > 1.3                |
| ld_inferiority                     | Inferiority | 2.5% probability of treatment benefit             |
| ld_equivalence                     | Equivalence | 90% probability between win ratio of 0.8 and 1.25 |


Simulations under the alternative hypothesis were run using the previously defined assumed rates:

|                  | Control | Active |
| ---------------- | ------- | ------ |
| Survival         | .85     | .9     |
| Days at home     | 67      | 78     |
| Amb Status Shift |         | 0.2    |


Additionally, a null hypothesis were also performed to see what type I error rates were.


`r total_sims` simulations were run for each scenario.

## Results

The tables below show the rates for the number of times each criteria is hit. The rates are cumulative - so if superiority is hit with 50, it will automatically hit at 100, 150, and 200.
Additionally branching logic is not implemented. For example if inferiority is hit at 50, the trial does not stop.

### Alternative Hypothesis Results

```{r}
#| cache: true
sim_results <- 1:total_sims |>
  purrr::set_names() |>
  purrr::map(function(x) {
    all_trial_data <- simulate_trial(n_per_arm = n_per_arm)
    data_subsets <- purrr::map(data_cuts, subset_trial, d = all_trial_data)
    freq_estimates <- data_subsets |>
      purrr::map(estimate_dataset) |>
      purrr::map(function(x) subset(x, term == "days_at_home_t7", select = c(estimate, std.error)))

    trial_output <- purrr::map(freq_estimates, function(x) {
      fit <- mod$sample(
        data = make_stan_data(x, prior_std = 1),
        seed = 123,
        chains = 1,
        parallel_chains = 1,
        refresh = 0,
        show_messages = FALSE
      )
      stan_success(fit)
    }) |>
      purrr::list_rbind(names_to = "analysis_amount")

    trial_output
  }) |>
  purrr::list_rbind(names_to = ".sim")

```

```{r}
summarize_results(sim_results) |>
  flextable::flextable()

```



## Null Hypothesis Results


```{r}
#| cache: true
null_sim_results <- 1:total_sims |>
  purrr::set_names() |>
  purrr::map(function(x) {
    all_trial_data <- simulate_trial(
      n_per_arm = n_per_arm,
      survival_prob = c(.85, .85),
      days_at_home_mean = c(70, 70),
      amb_status_latent_shift = 0
    )
    data_subsets <- purrr::map(data_cuts, subset_trial, d = all_trial_data)
    freq_estimates <- data_subsets |>
      purrr::map(estimate_dataset) |>
      purrr::map(function(x) subset(x, term == "days_at_home_t7", select = c(estimate, std.error)))

    trial_output <- purrr::map(freq_estimates, function(x) {
      fit <- mod$sample(
        data = make_stan_data(x, prior_std = 1),
        seed = 123,
        chains = 1,
        parallel_chains = 1,
        refresh = 0,
        show_messages = FALSE
      )
      stan_success(fit)
    }) |>
      purrr::list_rbind(names_to = "analysis_amount")

    trial_output
  }) |>
  purrr::list_rbind(names_to = ".sim")

```

```{r}
null_sim_results |>
  summarize_results() |>
  flextable::flextable()

```


